Meta-analysis

### 2019-11-20 04_Prep_data.Rmd
Correcting Variance formula
Some adjustments to sampling variance formulas and the incorporation of MSE into the slimmer dataset

# Place holder

@@

   #  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
   #  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
   #  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
   #  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
   #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
   MSE <-
      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
                                                                            Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
      if (j == 1) {
         Sv <-
            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
      }
      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
      # Balance equation
      Sv[j] = sqrt(MSE / (
         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])
      ))

@@

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
   "SamplingVariance"
```

## Yield gains  
Yield gains and yield gains proportional to the control.

@@

>>>>

@@

   #  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
   #  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
   #  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
   #  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
   #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
   V_yield <-
      (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
                                                                            Tcrit) ^ 2) / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
      if (j == 1) {
         Sv <-
            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
      }
      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
      # Balance equation
      # Sv[j] = V_yield / 
      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
      # 
      Sv[j] = V_yield / 
         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j]

      # Sv[j] = MSE / 
      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
      #

      ### -> This formula should be V = (n * (LSD/1.96)^2) / 2

@@

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
   "SamplingVariance"

## Yield saving  
Yield saving and Yield saving proportional to the control.

@@

```{r}

slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)

slimmer_PM_dat %>%
   ggplot(aes(y= grain_yield.t.ha, x = vi))+
   geom_point()
